Astropy - New software standards for a growing community

### 2017-09-20 main.tex
fix merge conflict issue

\section{Key features}

@@

\subsection{Coordinates}

start with short description of the astropy approach and features (JPL ephemerids, barycentric correction, proper motions, coordinate frames) then shows the tests. In particular, we had a discussion on problems with the definition of some coordinate system on the mailing list. Getting that discussion in here gives us a refereed paper to point to when we need to push the IAU to fix that.

@@

\subsubsection{NDDdata}

\subsubsection{Tables}
QTable is new, mixin columns for time and coordinates. Table operations were added in v0.3

>>>>

\section{Astropy Core Package v2.0}

@@

\subsection{Coordinates}
% Adrian & Erik

The \texttt{astropy.coordinates} subpackage ...

- Three-tiered structure for coordinates: representation, frame, skycoord
- With differential classes, frames support velocities
- Celestial coordinates, and local coordinates (via EarthLocation + Time)
- JPL ephemerids

start with short description of the astropy approach and features (JPL ephemerids, barycentric correction, proper motions, coordinate frames) then shows the tests.

In particular, we had a discussion on problems with the definition of some coordinate system on the mailing list. Getting that discussion in here gives us a refereed paper to point to when we need to push the IAU to fix that.

@@

\subsubsection{NDDdata}
% Matt C., Michael, or Steve C.

\subsubsection{Tables}
% Tom A.
QTable is new, mixin columns for time and coordinates. Table operations were added in v0.3
